Figure 3 - ChIP

### 2024-08-06 ms_figure_3_chip.Rmd
make SFig3 portrait

pd <- motifs |>
    select(name, total_hits, starts_with("bound_hits")) |>
    mutate(frac_bound_hits_any = (bound_hits_common.peaks.ubiquitous +
               bound_hits_common.peaks.frequent + bound_hits_specific.peaks) / total_hits,
           `Common (ubiquitous)` = bound_hits_common.peaks.ubiquitous / total_hits,
           `Common (frequent)` = bound_hits_common.peaks.frequent / total_hits,
           `Specific` = bound_hits_specific.peaks / total_hits) |>
    # arrange(desc(frac_bound_hits_any)) |>
    arrange(frac_bound_hits_any) |>
    mutate(name = factor(name, levels = name)) |>
    pivot_longer(cols = c("Common (ubiquitous)", "Common (frequent)",
                          "Specific"), names_to = "peak_set", values_to = "fraction_bound") |>
    mutate(peak_set = factor(peak_set, levels = c("Common (ubiquitous)", "Common (frequent)",
                          "Specific")))

(p_fracbound <- ggplot(pd, aes(name, fraction_bound, fill = peak_set)) +
        geom_col() +
        scale_y_continuous(expand = expansion(mult = 0),
                           labels = scales::label_percent()) +
        scale_fill_manual(values = peakset_colors) +
        labs(x = element_blank(),
             y = "Percent of motif sites",
             fill = element_blank()) +
        theme_cowplot(12) +
        theme(legend.position = "inside",
              legend.position.inside = c(0.05, 0.95),
              legend.justification.inside = c(0, 1),
              axis.text.x = element_text(angle = 90, hjust = 1, size = 8)) +
        guides(fill = guide_legend(ncol = 1)))
```

@@

```{r suppFig3}
#| fig.width: 11
#| fig.height: 9
#| warning: false

cowplot::plot_grid(
    cowplot::plot_grid(NULL, NULL, NULL, # space for labels
                       nrow = 1, labels = c("A", "B", "C"),
                       rel_widths = c(100, 100, 100)),
    cowplot::plot_grid(
        cowplot::plot_grid(gnmtracks2, NULL, ncol = 1, rel_heights = c(20, 1)),
        hm_motifs_long,
        p_fracbound,
        nrow = 1,
        labels = c("", "", "")
    ),
    nrow = 2,
    rel_widths = c(1),
    rel_heights = c(0.25, 9.75)
)
```

>>>>

pd <- motifs |>
    select(name, total_hits, starts_with("bound_hits")) |>
    mutate(frac_bound_hits_any = (bound_hits_common.peaks.ubiquitous +
               bound_hits_common.peaks.frequent + bound_hits_specific.peaks) / total_hits,
           `Common (ubiquitous)` = bound_hits_common.peaks.ubiquitous / total_hits,
           `Common (frequent)` = bound_hits_common.peaks.frequent / total_hits,
           `Specific` = bound_hits_specific.peaks / total_hits) |>
    arrange(desc(frac_bound_hits_any)) |>
    mutate(name = factor(name, levels = name)) |>
    pivot_longer(cols = c("Common (ubiquitous)", "Common (frequent)",
                          "Specific"), names_to = "peak_set", values_to = "fraction_bound") |>
    mutate(peak_set = factor(peak_set, levels = c("Common (ubiquitous)", "Common (frequent)",
                          "Specific")))

(p_fracbound <- ggplot(pd, aes(name, fraction_bound, fill = peak_set)) +
        geom_col() +
        scale_y_continuous(expand = expansion(mult = 0),
                           labels = scales::label_percent()) +
        scale_fill_manual(values = peakset_colors) +
        labs(x = element_blank(),
             y = "Percent of motif sites",
             fill = element_blank()) +
        theme_cowplot(12) +
        theme(legend.position = "inside",
              legend.position.inside = c(0.95, 0.75),
              legend.justification.inside = c(1, 1),
              axis.text.x = element_text(angle = 90, hjust = 1, size = 8)) +
        guides(fill = guide_legend(ncol = 1)))
```

@@

```{r suppFig3}
#| fig.width: 8.5
#| fig.height: 12.5
#| warning: false

cowplot::plot_grid(
    cowplot::plot_grid(NULL, NULL, # space for labels
                       nrow = 1, labels = c("A", "B"),
                       rel_widths = c(1, 1)),
    cowplot::plot_grid(
        cowplot::plot_grid(gnmtracks2, NULL, ncol = 1, rel_heights = c(20, 1)),
        hm_motifs_long,
        nrow = 1
    ),
    p_fracbound,
    nrow = 3,
    labels = c("", "", "C"),
    rel_heights = c(0.3, 9.7, 5.0)
)
```
